Evolution of Flare Activity in GKM Stars Younger than 300 Myr over Five Years of TESS Observations

### 2024-01-09 src/tex/ms.tex
post holiday changes

\newcommand{\angstrom}{\mbox{\normalfont\AA}}

@@

% Title
\title{Evolution of Flare Rates in GKM Stars Younger than 300 Myr}

% Author list
\author{Adina~D.~ Feinstein}
\altaffiliation{NHFP Sagan Fellow}
\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado
Boulder, UCB 600, Boulder, CO 80309}

@@

% Abstract with filler text
\begin{abstract}
Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events. Stellar magnetic activity  generally decreases as a function of both age and of Rossby number, $R_0$, a measure of the relative dominance of the convective and rotational dynamos. For those reasons, it is worthwhile analyzing the flare population level characteristics for young, rapidly rotating stars. With this motivation, we select a sample of stars that are either (i) members, (ii) candidate members or (iii) high-probability of being  members of 26 nearby young moving groups, clusters, or associations all known to be less than 300~Myr old that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at 2-minute cadence.  With this  sample of $\sim$~\textcolor{red}{n} stars younger than 300~Myr, we present detections and characterizations of the flare properties.  We identified \textcolor{red}{n} flares originating from \textcolor{red}{n} stars. Moreover, we robustly measured the rotation periods of $1,847$~stars. Finally, we measure the flare frequency distribution (FFD) slope as a function of both age and spectral type. We find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and does not evolve over 300~Myr. Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 - 300$~Myr are saturated out to $R_0 = 0.12$, which is consistent with other indicators of magnetic activity. We find the FFD slope for stars with $R_0 \leq 0.14$ are shallower than stars with $R_0 > 0.14$, suggesting the Coriolis force plays a role in generating more high-energy flares. We cross match our targets with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet flux. Finally, we compare the flare rates of planet hosting stars to comparable, larger samples of stars and find the majority of these stars are relatively flare quiet. This may impact the atmospheric evolution of young short-period exoplanets.

@@

Stellar flares are the radiation component of magnetic reconnection events \citep{}. Such events are readily seen on the Sun \citep{}, particularly now as we enter a maximum in the solar cycle \citep{}. Such events can be used to understand the magnetic activity of other stars \citep{}. Additionally, by studying stellar flares we can understand how these short-duration events may impact short-period exoplanet evolution \citep{}. While we cannot resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events. Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g. coronal mass ejections \citep{} or proton beams \citep{}. They can also inform our understanding of stellar plasma is displaced during these events \citep{}.

Photometric observations of stars are more readily available thanks to exoplanet missions, and allow us to statistically characterize flare rates and energies. Within time-series photometry, stellar flares can be identified by a sharp rise in the stellar flux and a subsequent exponential decay, corresponding to the cooling rate \citep{}. \textit{Kepler} provided long-baseline high-cadence observations used to identify stellar flares. There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.]{Hawley14, silverberg16}. \cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars. However, the flare frequency distribution (FFD) slope did not change significantly as a function of age. As a caveat, the ages of the stars were determined based on their rotation periods alone, relying on the assumption that gyrochronology alone accurately ages stars.

After the failure of two reaction wheels, \textit{Kepler} was repurposed to the \textit{K2} mission \citep{Howell14}. \textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters. \cite{ilin19} analyzed flares K and M stars in these clusters and measured FFD slopes of ...

More recently, the Transiting Exoplanet Survey Satellite \citep[TESS;][]{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less. Such an observing strategy has allowed for more detailed studies of young stellar flares from nearby young moving groups and associations, which are disperse in the sky \citep{}.

@@

In this section, we provide an overview of the methodology associated with this paper. The various methods described here are pertinent to the remainder of the paper. Specifically, we describe the sample selection in subsection \ref{subsec2:sample}, TESS light curve analysis in \ref{subsec2:TESS_lightcurve}, flare identification in subsection \ref{subsec2:Flareidentification}, flare models in \ref{subsec2:model}, flare quality checks in \ref{subsec2:qualitychecks}, and measurement of stellar rotaiton periods in \ref{subsec:prot}.

@@

In this paper, we select a sample of stars that have $<300$ Myr ages based on their affiliation with nearby young moving group, clusters and associations. This provides an independant constraint on the age, which is more robust than only using the rotational periods. Moreover, we select stars that have been observed with TESS with 2-minute cadence. With these criteria, we obtain light curves for a sample of 3,163 young stars in total.

With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}. In order to model the flare profile, we employ the analytical  model developed by \cite{tovar22}. This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy associated with each flare.

A primary goal of this paper is to  measure the evolution of the stellar flare rate and its dependance on the stellar age. Particularly, we are interested in this dependancy for
stars with ages $1 \leq t_\textrm{age} \leq 250$\,Myr. To this end, we used the MOCA Data Base
(Gagné et al. in prep.) to identify nearby young moving groups, associations,
and open clusters with known ages which satisfied our criteria. From this database we identified
 26~ unique groups from which we created our  sample of stars. The final selected targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii) candidate members. These rather stringent cuts resulted in a
 catalog of 30,889 stars across 26 associations. We summarize
the sample and   ages for each association (and therefore star)
in Table~\ref{tab:sample}.

\begin{deluxetable}{l r r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Adopted Ages of each Young Stellar Population and Number of
Stars per Group \label{tab:sample}}
\tablehead{
\colhead{Population} & \colhead{Age [Myr]} & \colhead{N$_\textrm{stars}$} &
\colhead{Ref.}
}
\startdata
AB Doradus  &  133$_{-20}^{+15}$  &  88  & 1 \\
Blanco 1 & 137.1$^{+7.0}_{-33}$ & 428 & 2\\
Carina  &  45  & 94  & 3\\
Carina-Musca & 32 & 35 & 4\\
Chamaeleon  &  5  &  424  & 5 \\
Columba  &  42  &  126  & 3\\
Greater Taurus Subgroup 5 & 8.5 & 56 & 4\\
Greater Taurus Subgroup 8 & 4.5 & 122 & 4\\
Lower Centaurus Crux & 15 & 761 & 6\\
MELANGE-1 & 250$_{-70}^{+50}$ & 19 & 7\\
Octans  &  35$\pm 5$ &   64  & 8 \\
Pisces Eridanis  &  120  &   219  & 9 \\
Pleiades & 127.4$^{+6.3}_{-10}$ & 1421 & 2\\
$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  625 & 2 \\
IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 160 & 2 \\
NGC 2451A & 48.5 & 59 & 4\\
Oh 59 & 162.2 & 62 & 10\\
Platais 9 & 50 & 124 & 11\\
RSG2 & 126 & 145 & 12\\
Theia 301  &  195  &  437 & 10\\
Theia 95  &  30.2  &  230 & 10\\
TW Hydrae  &  10  &  24  & 3\\
Upper Centaurus Lupus & 16 $\pm$ 2 & 696 & 6\\
Upper Scorpius  &  10  &  106  &  6\\
Vela-CG4  &  33.7  &  299  & 4\\
\hline
Total & & 6,824\\
\enddata
\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{galindo22}; (3) \citet{Bell15}; (4) \citet{kerr21}; (5) \citet{luhman07}; (6) \citet{pecaut16}; (7) \citet{tofflemire21}; (8) \citet{murphy15}; (9) \citet{curtis19}; (10) \citet{kounkel20}; (11) \citet{tarricq21}; (12) \citet{roser16}}
\end{deluxetable}

@@

As described in the previous subsection, we only select stars in our sample for which TESS light curves have been obtained with 2-minute cadance. The reason for doing this is so that we are able to resolve and accure accurately measure the energies of flares for each of these stars \citep{howard22}.
We crossmatched our sample with the TESS Input Catalog (TIC) based on their RA and Dec.
In order for a star to be considered as a member of the catalog, , we required that  the distance between the target and
the nearest TIC was within $<1"$.

This process provided  a final sample of 5,725 unique targets. These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67. These are the latest available sectors at the time that this analysis was performed. In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions of the final sample.  It is evident that  many targets exhibit strong tendency for proximitry towards the
northern and southern ecliptic poles (Figure~\ref{fig:sample}). Therefore, many  of these targets were observed
over multiple sectors all of which observed the ecliptic poles. The entirety of the available data yielded  a total of 17,964
light curves, an average of $\sim 3$ light curves per target (although with significant spread across targets).

\begin{figure}[ht!]
    %\script{sample.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/sample.pdf}
        \caption{
            Top: Distribution of our selected sample across the sky and colored by the adopted age of the association (see Table~\ref{tab:sample}). The all-sky coverage by TESS has unlocked new populations of stars to observe. We take advantage of this observing strategy to measure flare rates across 26 different nearby young moving groups, clusters, and associations. Bottom: Distribution of adopted effective temperatures, $T_\textrm{eff}$ [K] for stars in our sample. We include all stars with $T_\textrm{eff} \leq 6000$\,K.
        }
        \label{fig:sample}
    \end{centering}
\end{figure}

@@

Once we had the lightcurves for each target, we performed the following procedur to identify stellar flares. First, we implemented the machine learning flare-identification methods presented and described in
\cite{feinstein20}. This method relies on the fact that all flare events
have similar time-dependent morphologies. These flare-profiles can generally be described as a sharp rise followed by
 an exponential decay in the white light curve. The identification-technique implements  a convolutional neural network (CNN),
\texttt{stella} \citep{feinstein20}. The neural network was trained to identify flare events in TESS 2-minute data using a catalogue of flare events from
TESS Sectors 1 and 2 that were validated  by-eye
\citep{guenther19_flares}.

There are many benefits to using the CNN for stellar flare identification. Primarily, the CNN is advantageous because it is insensitive to the stellar baseline flux. This feature inherently stems from the fact that the network is trained to search \textit{only} based on flare morphology. It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself. One advantage of this is that rotational modulation peaks --- which are themselves  driven by
stellar heterogeneities ---
are not accidentally identified as flares. This is especially advantageous for our sample of young stars, which  readily exhibit rotational modulatioin and associated peaks  in their light curves.

Based on these advantages, the final compiled sample of flares is \textit{unbiased} towards low-amplitude/low-energy flares. It is important to note that these low-energy events are typically  not identified in traditional sigma-outlier identification
methods \citep{chang15}.

The \texttt{stella} CNN models calculates the probability that a data point in a light curve is associated with a flaring event. Specifically, it taakes the light curve (time, flux, flux error)
as an input and returns an array with values of [0,1], which are treated as
the probability a data point is (1) or is not (0) part of a flare. We ran every
light curve through 10 independant \texttt{stella} models to ensure that our statistics were accurate. We then averaged the output probabilities for each 10 model runs to be the final prediction per observation.

In order to identify a single flare event, the \texttt{stella} code uses the
predictions per data point to group together points. We modified this stage of identification slightly from the original flare-identification method. Specifically, we identified all data points with a probability of being associated with a flare of $P > 0.75$. Any data points that were within 4 cadences of each other were considered to be a single flare event. We did not consider any potential flares that had three or fewer points with $P > 0.75$. This was motivated by the fact that  sometimes a single-point outlier is assigned a high probability of being a flare. Therefore, we simply neglected these events. We assigned the probability of the whole flare event as the probability of the peak data point.

\begin{figure}[ht!]
    %\script{flare_distribution.py}
    \begin{centering}
        \includegraphics[width=0.9\linewidth]{figures/flare_distribution.pdf}
        \caption{
            High level summary of the demographics of flares in our sample. Top:
            The number of flares identified compared to the number of stars in
            each nearby young moving group, cluster, or association. A one-to-one
            relationship is expected. Middle: The distribution measured TESS energies
            and equivalent durations of flares in our sample, colored by the probability
            of the flare as identified with \texttt{stella}. Bottom: Same as the
            middle plot, except colored by the $T_\textrm{eff}$ [K] of the star.
            We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
        }
        \label{fig:flare_distribution}
    \end{centering}
\end{figure}

@@

As described in the previous subsection, flares are well-described in light curves as a sudden increase in flux followed by an exponential decay. For this paper, we used the analytical flare model,Llamaradas Estelares which was  presented in
\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}. We used these models to fit the flares and extract the flare parameters in all of the light curves of our sample. This model builds upon the model presented
in \cite{davenport14}. Specifically, it includes the convolution of a Gaussian with a
double exponential model in the flare profile.

The analytical model is robust in that it is able to accounts for multiple inherent features of flares. Specifically, it can incorporate the flare (i) amplitude,
 (ii) heating timescale, (iii) rapid cooling phase timescale, and (iv) slow cooling phase
timescale . We implemented a nonlinear least squares
optimization to fit for the time of the flare peak ($t_\textrm{peak}$),
full width at half maximum (FWHM), and the amplitude ($A$) of each flare
in the sample.  We combine the model with a second-order polynomial fit to
a 1.2-hour baseline before and after the flare  during only the fitting stage. This was implemented in order to account for any rotational modulation, and therefore  was particularly relevant for the rapid rotators.

We calculated the equivalent duration, ED, of the flare by performing a numerical integration  of the flare flux with respect to time. We calculate the flare energy, $E_\textrm{flare}$, using,

\begin{equation}\label{eq:Eflare}
    E_\textrm{flare} = L_\star \, A \, \textrm{ED} \, s \, .
\end{equation}
In equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is the Planck function. We assume that the flare temperature is 9000~K \citep{}.

@@

In this subsection, we describe the methodology we employ to ensure that flares identified by the CNN are high quality. The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2. However, the noise properties are variable aross sectors in TESS data. The CNNs are therefore unable to accurately
account for and capture  this variation when operating on different sectors. Moreover, the original CNNs were only trained on a sample of 1,228 stars. This sample  does not necessarily encapsulate all or even a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast rotators with rotation periods $P_\textrm{rot} < 1$~day. We  therefore apply  additional
quality checks to ensure our flare sample has little to no contamination
from other sources.

>>>>

%%%%%%% COMMANDS FOR THIS PAPER
\newcommand{\angstrom}{\mbox{\normalfont\AA}}
\newcommand{\nflares}{26,355}
\newcommand{\nflarestars}{3,160}
\newcommand{\nstars}{6,824}
\newcommand{\nprot}{1,847}

@@

% Title
\title{Evolution of Flare Activity in GKM Stars Younger than 300 Myr over Five Years of TESS Observations}

\shorttitle{Evolution of young stellar flare rates}
\shortauthors{Feinstein et al.}

\author[0000-0002-9464-8101]{Adina~D.~Feinstein}
\altaffiliation{NHFP Sagan Fellow}
\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado Boulder, UCB 600, Boulder, CO 80309}

@@

\author[0000-0002-1002-3674]{Kevin~France}
\affiliation{Laboratory for Atmospheric and Space Physics, University of Colorado Boulder, UCB 600, Boulder, CO 80309}
\affiliation{Department of Astrophysical and Planetary Sciences, University of Colorado, UCB 389, Boulder, CO 80309, USA}
\affiliation{Center for Astrophysics and Space Astronomy, University of Colorado, 389 UCB, Boulder, CO 80309, USA}

\author[0000-0002-2592-9612]{Jonathan Gagné}
\affiliation{Planétarium Rio Tinto Alcan, Escape pour la Vie, 4801 av. Pierre-de Coubertin, Montréal, Québec, Canada}
\affiliation{Institute for Research on Exoplanets, Université de Montréal, Départment de Physique, C.P. 6128 Succ. Centre-ville, Monetréal, QC H3C 3J7, Canada}

\author[0000-0001-7458-1176]{Adam~Kowalski}
\affiliation{Department of Astrophysical and Planetary Sciences, University of Colorado, UCB 389, Boulder, CO 80309, USA}
\affiliation{National Solar Observatory, University of Colorado Boulder, 3665 Discovery Drive, Boulder CO 80303, USA}

% Abstract with filler text
\begin{abstract}
Stellar flares are short-duration ($<$\,hours) bursts of radiation associated with surface magnetic reconnection events. Stellar magnetic activity generally decreases as a function of both age and Rossby number, $R_0$, a measure of the relative dominance of the convective and rotational dynamos. However, without young stars have been overlooked in flare studies due to lack of long baseline observations and challenges with flare-detection methods. With this motivation, we select a sample of stars that are either (i) members, (ii) candidate members or (iii) have a high-probability of being  members of 26 nearby young moving groups, clusters, or associations all known to be less than 300~Myr old that have been observed by the Transiting Exoplanet Survey Satellite (TESS) at 2-minute cadence.  With this sample of \nstars\ stars younger than 300~Myr, we identified \nflares\ flares originating from \nflarestars\ stars. Moreover, we robustly measured the rotation periods of \nprot~stars. We measure the flare frequency distribution (FFD) slope as a function of both age and spectral type and find the FFD slope, $\alpha$, saturates for all spectral types at $\alpha = -0.5$ and is constant over the 300~Myr window studied here. Additionally, we find that $R_0$ and flare rate for stars $t_\textrm{age} = 100 - 300$~Myr are saturated out to $R_0 = 0.14$, which is consistent with other indicators of magnetic activity. We cross match our targets with \textit{GALEX} and find no correlation between flare rate and Far- and Near-Ultraviolet flux. We compare the flare rates of planet hosting stars to comparable, larger samples of stars and find the majority of planet-hosting stars are relatively flare quiet. This may impact the atmospheric evolution of young short-period exoplanets. Finally, we detect evidence of stellar flare variations across five years of TESS data in eleven young stars, likely as a result of longer timescale stellar cycles.

@@

Stellar flares are the radiation component of magnetic reconnection events \citep{}. Such events are readily seen on the Sun \citep{}, particularly now as we enter a maximum in the solar cycle \citep{}. Such events can be used to understand the magnetic activity of other stars \citep{}. Additionally, by studying stellar flares we can understand how these short-duration events may impact exoplanet evolution \citep{}. While we cannot angularly resolve stellar flare events on other stars, we can detect and characterize both spectroscopic and photometric signatures of such events. Spectroscopic characterization of stellar flares inform our understanding of non-thermal processes affiliated with such events, e.g. coronal mass ejections \citep{} or proton beams \citep{}. They can also inform our understanding of stellar plasma is displaced during these events \citep{}.

Photometric observations of stars are more readily available thanks to exoplanet transit discovery missions, and allow us to statistically characterize flare rates and energies. NASA's \textit{Kepler}, \textit{K2}, and the Transiting Exoplanet Survey Satellite (TESS) missions have provided a wealth of stellar variability data in addition to their primary objective of detecting transiting exoplanets.  Within time-series photometry, stellar flares can be identified by a sharp rise in the stellar flux and a subsequent exponential decay, corresponding to the cooling rate \citep{}. \textit{Kepler} \citep{Borucki10} provided long-baseline high-cadence observations used to identify stellar flares. There has been extensive studies of flares in \textit{Kepler} data, from the statistics of superflares on solar-type stars \citep[e.g.][]{notsu13, shibayama13, maehara15, okamoto21} to low-mass stars \citep[e.g.][]{Hawley14, silverberg16}. \cite{davenport19} found that flare activity decreased with increasing rotation period for 347 GKM stars. However, the flare frequency distribution (FFD) slope did not change significantly as a function of age. As a caveat, the ages of the stars were determined based on their rotation periods, relying on the assumption that gyrochronology alone accurately ages stars.

\textit{K2} provided 70-day baseline observations for a handful of young stars in groups such as Upper Scorpius,  Pleiades, Hyades, and Praespe clusters. \cite{ilin19, ilin21} analyzed flares K and M stars in these clusters and found that the overall flare activity decreased as a function of age. This relationship was steeper for more massive stars in the sample. \cite{paudel18} surveyed 10 M6 - L0 dwarfs observed with \textit{K2} and found the L0 dwarf had a much shallower FFD than the M dwarfs. On average, they found that very young targets, defined by the tangential velocity of the star, overall had more flares.

More recently, TESS \citep{ricker15} has provided near all-sky photometric observations at 30-minute cadence or less. Such an observing strategy has allowed for more detailed studies of young stellar flares from nearby young moving groups and associations, which are disperse in the sky \citep{gagne18}. These new data have allowed for detailed studies of individual stars, for example characterizing eight superflares ($E_f > 10^{34}$~erg) on the young star AB Doradus over $\sim 60$ days of continuous observations \citep{schmitt19}.

The 11-year solar activity cycle represents a change in the magnetic activity of the Sun, and manifests itself in a variety of observables e.g., an increase in the total number of sunspots \citep{clette14, kilcik14}, an increase in the number of flares and coronal mass ejections \citep{crossby93, webb94, lin23}, and an increase in the total solar irradiance \citep{lean1987}. The majority of insights we have gained in long-term activity cycles on other stars is through photometric monitoring and spectroscopic monitoring \citep{saar99}. \cite{lehtinen16} collected 16 to 27 years of B- and V-band photometry for 21 young active solar-type stars. They found evidence of long-term stellar activity cycles in 18 targets following as $P_\textrm{rot}/P_\textrm{cycle} \propto R_0^{-1}$, where $P_\textrm{rot}$ is the rotation period, $P_\textrm{cycle}$ is the period of the stellar activity cycle, and $R_0$ is the Rossby number. Additionally, 50 years of spectroscopic observations of HD~166620 from the Mount Wilson Observatory and Keck revealed both a $\sim 16$~year periodicity in emission from the core of the \ion{Ca}{2} H and K lines \citep{olah16} and evidence that this star entered a grand minima \citep{baum22}. A more complete review on the state of stellar activity cycles can be found by \cite{jeffers23} and \cite{isik23}.

In addition to photometric and spectroscopic observations, solar flares trace the length of the solar activity cycle. The high-cadence observations from \textit{Kepler} (4-year baseline) and TESS (currently 5-year baseline) are providing data sufficient for searching for stellar activity cycle from the variations in stellar flare rates. \cite{davenport20} demonstrated that the flare rate and FFDs of GJ~1234 has not changed appreciably over 10~years of observations with both \textit{Kepler} and TESS. On the other hand, \cite{scoggins19} found that  KIC 8507979, an M3V star, showed a clear decline in flare rate and change in FFD over 4-years of \textit{Kepler} observations. While it is not expected to find flare rate and distribution variations in all stars given detection limitations, KIC 8507979 demonstrates the ability to study long-term flare variability as a potential tracer for stellar activity cycles.

@@

In this section, we provide an overview of the methodology associated with this paper. Specifically, we describe the sample selection in subsection \ref{subsec2:sample}, TESS light curve analysis in \ref{subsec2:TESS_lightcurve}, flare identification in subsection \ref{subsec2:Flareidentification}, how we fit for flare parameters in \ref{subsec2:model}, flare quality checks in \ref{subsec2:qualitychecks}, and measuring stellar rotation periods in \ref{subsec:prot}.

@@

A primary goal of this paper is to measure the dependence of the stellar flare rates on stellar age. Particularly, we are interested in this dependency for stars with ages $1 \leq t_\textrm{age} \leq 300$\,Myr. To this end, we used the MOCA Data Base (Gagné et al. in prep.) to identify nearby young moving groups, associations, and open clusters with known ages which satisfied our criteria. From this database we identified 26~ unique groups from which we created our sample of stars. The final selected targets were required to be: (i) confirmed members, (ii) high-likelihood candidate members, or (iii) candidate members. Membership to these groups has been primarily determined using kinematic information from \textit{Gaia} \citep{gaia16, gaia18}. These rather stringent cuts resulted in a catalog of 30,889 stars across 26 associations. We summarize the sample and ages for each association (and therefore star) in Table~\ref{tab:sample}.

%With these stars selected, we then run the convolutional neural network, \texttt{stella}, on each light curve to identify stellar flares \citep{stella_joss}. In order to model the flare profile, we employ the analytical model developed by \cite{tovar22}. This model is able to simultaneously (i) fit the flares and  (ii) measure the equivalent duration and energy associated with each flare.

\begin{deluxetable}{l r r r r r}[!ht]
\tabletypesize{\footnotesize}
\tablecaption{Adopted Ages of each Young Stellar Population and Number of
Stars per Group \label{tab:sample}}
\tablehead{
\colhead{Population} & \colhead{Age [Myr]} & \colhead{N$_\textrm{stars}$} &
\colhead{Ref.}
}
\startdata
AB Doradus  &  133$_{-20}^{+15}$  &  88  & 1 \\
Blanco 1 & 137.1$^{+7.0}_{-33}$ & 428 & 2\\
Carina  &  45$\pm 9$  & 94  & 3\\
Carina-Musca & 32 & 35 & 4\\
Chamaeleon  &  5  &  424  & 5 \\
Columba  &  42  &  126  & 3\\
Greater Taurus Subgroup 5 & 8.5 & 56 & 4\\
Greater Taurus Subgroup 8 & 4.5 & 122 & 4\\
Lower Centaurus Crux & 15 & 761 & 6\\
MELANGE-1 & 250$_{-70}^{+50}$ & 19 & 7\\
Octans  &  35$\pm 5$ &   64  & 8 \\
Pisces Eridanis  &  120  &   219  & 9 \\
Pleiades & 127.4$^{+6.3}_{-10}$ & 1421 & 2\\
$\alpha$ Persei  &  79$_{-2.3}^{+1.5}$  &  625 & 2 \\
IC 2602 system &  52.5$_{-3.7}^{+2.2}$  & 160 & 2 \\
NGC 2451A & 48.5 & 59 & 4\\
Oh 59 & 162.2 & 62 & 10\\
Platais 9 & 50 & 124 & 11\\
RSG2 & 126 & 145 & 12\\
Theia 301  &  195  &  437 & 10\\
Theia 95  &  30.2  &  230 & 10\\
TW Hydrae  &  10  &  24  & 3\\
Upper Centaurus Lupus & 16 $\pm$ 2 & 696 & 6\\
Upper Scorpius  &  10  &  106  &  6\\
Vela-CG4  &  33.7  &  299  & 4\\
\hline
Total & & \nstars\\
\enddata
\tablecomments{Age references: (1) \citet{gagne18_abdmg}; (2) \citet{galindo22}; (3) \citet{Bell15}; (4) \citet{kerr21}; (5) \citet{luhman07}; (6) \citet{pecaut16}; (7) \citet{tofflemire21}; (8) \citet{murphy15}; (9) \citet{curtis19}; (10) \citet{kounkel20}; (11) \citet{tarricq21}; (12) \citet{roser16}}
\end{deluxetable}

@@

As described in the previous subsection, we select stars in our sample for which TESS light curves have been obtained with 2-minute cadence. The reason for doing this is so that we are able to resolve and accurately measure the properties of flares for each of these stars \citep{howard22}. We cross-matched our sample obtained with the MOCA Database with the TESS Input Catalog (TIC) based on their Gaia DR2 RA and Dec. We required that the distance between the target and the nearest TIC target was within $<1"$.

This process provided a final sample of \nstars\ unique targets. These targets have each been observed at a 2-minute cadence between TESS Sector 1 and Sector 67; Sector 67 was the latest available sectors at the time that this analysis was performed. In Figure ~\ref{fig:sample}, we show the distribution of the on sky positions and effective temperatures, $T_\textrm{eff}$, of the final sample. We use $T_\textrm{eff}$ as our stellar characterization metric over the standard $M_\star$ because $\sim 600$ stars in our sample are lacking mass information in the TIC.  It is evident that  many targets exhibit strong tendency for proximity towards the
northern and southern ecliptic poles (Figure~\ref{fig:sample}). Therefore, many of these targets were observed
over multiple sectors. The entirety of the available data yielded 17,964 light curves processed by the Science Processing Operations Center (SPOC) pipeline \citep{jenkins16}. Our sample has an average of $\sim 3$ light curves per target (although with significant spread across targets). For our analysis, we used the SPOC-processed SAP\_FLUX.

\begin{figure}[ht!]
    \script{sample.py}
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/sample.pdf}
        \caption{
            Top: Distribution of our selected sample across the sky and colored by the adopted age of the association (see Table~\ref{tab:sample}). The all-sky coverage by TESS has unlocked new populations of stars to observe. We take advantage of this observing strategy to measure flare rates across 26 different nearby young moving groups, clusters, and associations. Bottom: Distribution of adopted effective temperatures, $T_\textrm{eff}$ [K] for stars in our sample. We include all stars with $T_\textrm{eff} \leq 6000$\,K.
        }
        \label{fig:sample}
    \end{centering}
\end{figure}

@@

Once we had the light curves for each target, we performed the following procedure to identify stellar flares. First, we implemented the machine learning flare-identification methods presented and described in \cite{feinstein20}. This method relies on the fact that all flare events have similar time-dependent morphologies. These flare-profiles can generally be described as a sharp rise followed by an exponential decay in the white light curve. This identification-technique implements the convolutional neural network (CNN),
\texttt{stella} \citep{feinstein20}. The neural network was trained to identify flare events in TESS 2-minute data using a catalogue of flare events from TESS Sectors 1 and 2 that were validated  by-eye
\citep{guenther19_flares}.

There are many benefits to using the CNN for stellar flare identification. Primarily, the CNN is advantageous because it is insensitive to the stellar baseline flux. This feature inherently stems from the fact that the network is trained to search \textit{only} based on flare morphology. It is therefore relatively insensitive to the absolute flux levels, so long as the inherent noise does not overwhelm the signal itself. This means that rotational modulation peaks --- which are themselves driven by
stellar heterogeneities --- are not accidentally identified as flares. This is especially advantageous for our sample of young stars, which  readily exhibit rotational modulation in their light curves.

Based on these advantages, the final compiled sample of flares is \textit{unbiased} towards low-amplitude/low-energy flares. It is important to note that these low-energy events are typically not identified in traditional sigma-outlier identification
methods \citep{chang15}. The \texttt{stella} CNN models calculates the probability that a data point in a light curve is associated with a flaring event. Specifically, it takes the light curve (time, flux, flux error) as an input and returns an array with values of [0,1], which are treated as the probability a data point is (1) or is not (0) part of a flare. We ran every light curve through 10 independent \texttt{stella} models and averaged the outputs to ensure that our statistics were accurate. We note that in this processing, the CNN ignores 200-minutes before and after any gaps in the data. Therefore, any flares which occur during these times are not identified.

In order to identify a single flare event, the \texttt{stella} code uses the predictions per data point to group together points. We modified this stage of identification slightly from the original flare-identification method. Specifically, we identified all data points with a probability of being associated with a flare of $P > 0.75$. Any data points that were within 4 cadences of each other were considered to be a single flare event. We did not consider any potential flares that had three or fewer points with $P > 0.75$. This was motivated by the fact that  sometimes a single-point outlier is assigned a high probability of being a flare. Therefore, we neglected these events. We assigned the probability of the whole flare event as the probability of the peak data point.

\begin{figure}[ht!]
    \script{flare_distribution.py}
    \begin{centering}
        \includegraphics[width=0.9\linewidth]{figures/flare_distribution.pdf}
        \caption{
            High level summary of the demographics of flares in our sample. Top: The number of flares identified compared to the number of stars in each nearby young moving group, cluster, or association. A one-to-one relationship is expected. Middle: The distribution measured TESS energies
            and equivalent durations of flares in our sample, colored by the probability of the flare as identified with \texttt{stella}. Bottom: Same as the middle plot, except colored by the $T_\textrm{eff}$ [K] of the star. We limit our sample to stars with $T_\textrm{eff} \leq 6000$\,K.
        }
        \label{fig:flare_distribution}
    \end{centering}
\end{figure}

@@

As described in the previous subsection, flares are well-described in light curves as a sudden increase in flux followed by an exponential decay. For this paper, we used the analytical flare model, Llamaradas Estelares which was presented in
\cite{tovar22}\footnote{\url{https://github.com/lupitatovar/Llamaradas-Estelares}}, to fit the flares and extract the flare parameters in all of the light curves of our sample. This model builds upon the model presented in \cite{davenport14}. Specifically, it includes the convolution of a Gaussian with a double exponential model in the flare profile.

The analytical model is robust in that it is able to accounts for multiple inherent features of flares. Specifically, it can incorporate the flare (i) amplitude, (ii) heating timescale, (iii) rapid cooling phase timescale, and (iv) slow cooling phase timescale. We implemented a nonlinear least squares optimization to fit for the time of the flare peak ($t_\textrm{peak}$), full width at half maximum (FWHM), and the amplitude ($A$) of each flare in the sample.  We combine the model with a second-order polynomial fit to a 1.2-hour baseline before and after the flare  during only the fitting stage. This was implemented in order to account for any slope due to rotational modulation, and therefore was particularly relevant for the rapid rotators ($P_\textrm{rot} < 2$~days).

We calculated the equivalent duration, ED, of the flare by integrating the quiescent-normalized flare flux with respect to time. We calculate the flare energy, $E_\textrm{flare}$, using,

\begin{equation}\label{eq:Eflare}
    E_\textrm{flare} = L_\star \, A \, \textrm{ED} \, s \, .
\end{equation}
In Equation \ref{eq:Eflare}, $L_\star$ is the luminosity of the star and $s$ is a scaling factor defined as $s = B_\lambda(T_\textrm{eff}) / B_\lambda(T_\textrm{flare})$, where $B_\lambda(T)$ is the Planck function. We assume that the flare temperature is 9000~K \citep{kretzschmar11}. Although 900

@@

In this subsection, we describe the methodology we employ to ensure that flares identified by the CNN are high quality. The \texttt{stella} CNNs were trained on data from TESS Sectors 1 and 2. However, the noise properties are variable across sectors in TESS data. The CNNs are therefore unable to accurately
account for and capture  this variation when operating on different sectors. Moreover, the original CNNs were only trained on a sample of 1,228 stars. This sample  does not necessarily encapsulate all or even a sufficient distribution  of variable stars types, such as eclipsing binaries, RR Lyraes, and fast rotators with rotation periods $P_\textrm{rot} < 1$~day. We therefore apply additional
quality checks to ensure our flare sample has little to no contamination from other sources.
